Oasis or Mirage? \\ \large{Trade Network Propagation of Deforestation}

### 2024-08-26 paper/main.tex
modify the network figs

\title{Oasis or Mirage? \\ Trade Network Propagation of Deforestation}
\author{Tomoki Nishiyama\footnote{Department of Economics, the University of Tokyo. \\ e-mail address: nishiyama-tomoki@g.ecc.u-tokyo.ac.jp \\ I thank Yasuyuki Sawada (a main advisory professor of this thesis), Michihiro Kandori, and all the participants of their seminar for helpful discussion. I am also grateful to Shotaro Beppu, Yutao Chen, and Yuto Iwamoto for meaningful comments and supports.}}
\date{January 2024}
\maketitle

\begin{abstract}
    Log production is destroying forests around the world and contributing to global warming. To address deforestation, various countries have begun to adopt policies to restrict log exports. However, even if one country restricts log exports, the countries that have been importing logs may increase their log production to compensate for their previous imports. It is also possible that other countries will increase their log exports to the log consuming countries. In this case, one country's log export restrictions could induce deforestation in other countries through trade networks. In this paper, Ifocus on two policies, Russia's log export restrictions in 2007 and Myanmar's log export ban in 2014, to demonstrate how these policies affect the log industry in other countries through trade networks. We find that when one country restricts log exports, log production increases in their previously main export destination. This result suggests that through a network of trade, one country's pro-environmental policies can cause environmental damage in other countries.
\end{abstract}

\textit{
    A king is wandering in the desert. There used to be a forest in this desert. However, due to the mass production of logs, the former forest has been lost and has become a desert. The once cool forest is now a scorching desert with no water to be found no matter how far one walks. The king, who is about to collapse, finds something like water in the distance. The king says, "There is an oasis spreading out over there. There must be water. There must be trees. We can regenerate the forest from there." And he starts running. But, is that water really an oasis? Is it not a mirage?
}
\section{Introduction}
Deforestation is an urgent issue on this planet: 50\% of forests has already been lost since 1990 (DATA). Deforestation is causing devastation of the global environment. Deforestation accounts for 12-20\% of global greenhouse gas emissions, as it reduces the capacity to absorb carbon dioxide through plants' photosynthesis and contributes to climate change. Deforestation also causes loss of biodiversity because forests are home to a wide variety of plants and animals. The extraction of timber to produce forest products is one of the main causes of deforestation. To address this serious problem, some countries have banned log exports since the 1980s. For example, Myanmar, which has destroyed half of its tropical forests since 1960 and worked as the world's third largest supplier (DATA), banned log exports in 2014. \\

@@

Using annual trade flow and production data of forestry industries, I employ shift-share design to empirically demonstrate effects of supply shock triggered by the ban of log exports. I regress outcome of each country on how much the country is exposed to the supply shock. The exposure to the shock is measured with interaction of two parts. The first part called ``shift'' is a measure of how much export-restricting country reduces their export to the rest of the world with the restriction. The second part called ``share'' is a measure of how much each country has been dependent on a specific market or industry before the restriction. Combining these two parts, Iobtain measure of how much each country is exposed to the Russia or Myanmar's export restriction policy. By using this shift-share approach, I find that when log export restrictions are imposed in a country, log production increases in the country with the larger exposure to that supply shock, i.e., the country that was the export-restricting country's major export destination. This indicates that a country's log export restrictions contribute to deforestation in its major trading partners. On the other hand, for countries that exported to markets similar to that export-restricting country, there was no significant response in terms of production, export volume, or export value to the export-restriction shock. These results suggest that an pro-environmental policy in one country to protect its own forest has effect to propagate deforestation to their previous trade partners. This implicates that an efficacy of one country's forest protection can be crowded out by the spillover effects. It emphasizes that one government policy to protect its own forest is not sufficient to tackle with global environmental issue.\\

@@

As for the empirical method to examine propagation of a supply shock, I refer to recent growing literature of network analysis in economics. \cite{acemoglu2012network} firstly introduces the analysis of how shock on an agent propagates to the other agents throughout network between agents. Based on this strand, various papers discuss how a shock to a specific firms affects the other firms that do not directly suffer from the shock through production supply chain. For example, \cite{barrot2016input} and \cite{carvalho2021supply} examine how shocks of the Eastern Japan Great Earthquake affects firms that are located far from the damaged area through their supply chain networks. I follow shift-share approach of \cite{huneeus2018production} to empirically show the network propagation effects of one country's pro-environmental policy on the other countries.\\

The remainder of this paper is organized as follows. Section 2 describes how I construct trade network flow data for forest products. Section 3 provides an overview of two trade restriction policies (Russia in 2007 and Myanmar in 2014) and explains how these policies are exogeneous shocks for other countries. Section 4 presents a sketch of the network data to give an overall picture of the trade network. Based on some basic facts explained in Section 4, Section 5 presents a simple model for constructing hypotheses on how one country's policy affects other countries. Based on the theoretical predictions, Section 6 and 7 presents empirical results. Section 6 describes impacts of export restriction policy on the country's log trade partners. Then, Section 7 presents impacts on trade competitors that supply logs to the Russia's (or Myanmar's) trade partners. Section 8 discusses interpretation of the empirical results. Finally, Section 9 presents the conclusions. Extensions of the theoretical model and robustness checks of the empirical results are in the appendix.\\

@@

@@

\subsection{Russia's log export restriction in 2007}
Russia developed the largest coniferous forest in the world, the Siberian ``taiga'', which accounted for half of the world's supply of coniferous wood.  To cope with the deforestation and to promote domestic wood processing industry, Russian government imposed an export tax of 6.5\% in July 2007, rising to 20\% on July 2007 and 25\% in April 2008 on logs exported from Russia. This restriction on log exports was introduced due to the Russian domestic situation. Additionally, as METI points out, the new Russian Forest Code, which was base of these export tax policies, was founded in December 2006. This haste of policy interventions supports my assumption that the policy was exogeneous shock for the rest of the world. \\

Fig \ref{fig:shock_russia} shows significance of this Russian supply shock. Panel A represents time-series of import price, import quantity, and import value for coniferous roundwood. First, let us see Panel A. Each gray line represents the average price at which roundwood produced in each country is imported into the rest of the world. The blue line represents the average price at which roundwood produced in Russia is imported into countries other than Russia. In the same way, Panels B and C show the average import volume and total import value, respectively, of roundwood produced in each country and imported into the rest of the world.

Panel A shows that Russia's restriction on log exports in 2007 increases the average price of roundwood imports from Russia about 1.1 $\sim$ 1.4 times. This increase is consistent with the export tax rate. In addition to the effect on price, Panel B describes that the policy dramatically reduces the average quantity of roundwood imports from Russia by almost half. Panel C shows the policy leads to a rapid decrease in value of imports from Russia. In other words, the export restriction policy in 2007 has significant impact on the supply from Russia to the rest of the world market.

@@

We can consider this export ban as an exogenous supply shock for the rest of the world. That is because the prohibition was due to the situation of Myanmar's country, which is not related to the other countries' situation. Fig \ref{fig:shock_Myanmar} shows significance of the supply shock. Panel A represents time-series of import price, import quantity, and import value for non-coniferous and non-tropical roundwood. First, let us see Panel A. Each gray line represents the average price at which roundwood produced in each country is imported into the rest of the world. The blue line represents the average price at which roundwood produced in Myanmar is imported into countries other than Myanmar. In the same way, Panels B and C show the average import volume and total import value, respectively, of roundwood produced in each country and imported into the rest of the world.\\

@@

\section{Sketch of the Trade Network of Logs}
This section provides descriptive statistics to convey whole picture of the trade network data. First, I show cross-sectional summary statistics of roundwoods in 2018 with Table \ref{tab:summary_stat}. The summary statistics of roundwood export / import prices are presented in Table \ref{tab:summary_stat_price} in the Appendix. Based on these summary statistics, I presents several facts which describe the trade networks.\\

@@

\textit{\textbf{Fact 1:} Most of the roundwood production are supplied to the domestic market.} \\
Table \ref{tab:summary_stat} shows that around 10\% of the roundwood production are used for international trade and the rest 90\% are consumed in the domestic market. Figure \ref{tab:summary_stat_price} shows the long term trend of production and export of roundwoods. In any period, around 90 \% of the production is consumed in the domestic market\footnote{There is a jump in the export quantity of non-coniferous non-tropical roundwood in 2004. This might be due to errors of the original FAOSTAT dataset.}.

@@

\textit{\textbf{Fact 2:} Roundwood is used as intermediate inputs of forestry products.} \\
Roundwood is used as intermediate input goods of various forestry product, such as sawn wood, plywood, pulp, and wood chip. Table \ref{tab:intermediate_input} shows relationship between quantity of forestry products made in each country and quantity of roundwood produced for domestic market and roundwood imported from foreign suppliers. As a control, I include lagged GDP on the right-hand side. There are positive relationship between quantity of roundwoods and quantity of forestry products. This result is consistent with the fact that roundwoods are used as intermediate inputs of forestry products.

@@

 \textit{\textbf{Fact3:} The distribution of active export / import links (links with positive export / import quantity) is right-skewed.}\\
 I construct bipartite graph consisted of around 160 importer countries and 160 exporter countries. However, not all the links between potential importer countries and exporter countries are not active. In other words, some countries do not export roundwood at all to some other countries. To examine the number of active links of roundwood trade, I present histograms in Figure \ref{fig:num_of_trade_links}. First, in both export and import of any roundwood, the distribution has a long tail on the right side. In addition, the number of countries with zero links are larger in exports than in imports. This is consistent with the uneven distribution of forest resources over countries due to different climate or areas.

 \begin{figure}[H]
    \centering
    \caption{Number of Roundwood Trade Links in 2018}
    \subfigure[][Export Links]{\centering \includegraphics*[bb=0 0 1000 1000, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/num_links/num_links_exp.png"}}
    \subfigure[][Import Links]{\centering \includegraphics*[bb=0 0 1000 1000, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/num_links/num_links_imp.png"}}
    \caption*{\small{The left panel is a histogram of number of links for roundwood exports, and the right panel is a histogram of number of links for roundwood imports. The unit is country-level, and there are 164 countries for coniferous roundwood, 166 countries for non-coniferous non-tropical roundwood, and 160 countries for non-coniferous tropical roundwood.}}
    \label{fig:num_of_trade_links}
\end{figure}

@@

The results of this decomposition in 2018 are displayed in Table \ref{tab:decomp_exp} and \ref{tab:decomp_imp}. ``Links'' indicates a esimate of $\beta_1$ and ``Average'' indicates a estimate of $\beta_2$. These results suggest that around $50 \sim 60$ \% of the variation of the export (import) value is explained by the variation of average export (import) value per link. In other words, more than half of the variation of the export (import) comes from variation of the intensive margin.

\begin{table}[htbp]
    \centering
    \caption{Cross-sectional Decomposition of Countries' Log Export Value}
    \begin{tabular}[t]{lcccccc}
    \toprule
    \textit{log type:} &  \multicolumn{2}{c}{Coniferous}&  \multicolumn{2}{c}{Non-conif Non-tropical}&  \multicolumn{2}{c}{Non-conif tropical}\\
    \midrule
      & (1) & (2) & (3) & (4) & (5) & (6)\\
      \textit{Dependent Var:}& Links & Average & Links & Average & Links & Average \\
    \midrule
    log(Export Value)  & \num{0.390}*** & \num{0.610}*** & \num{0.412}*** & \num{0.588}*** & \num{0.379}*** & \num{0.621}***\\
    & (\num{0.010}) & (\num{0.010}) & (\num{0.010}) & (\num{0.010}) & (\num{0.013}) & (\num{0.013})\\
   \midrule
   Num.Obs. & \num{95} & \num{95} & \num{120} & \num{120} & \num{102} & \num{102}\\
   R2 & \num{0.899} & \num{0.956} & \num{0.919} & \num{0.959} & \num{0.894} & \num{0.957}\\
   \bottomrule
   \multicolumn{7}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
   \end{tabular}
   \label{tab:decomp_exp}
   \end{table}

\begin{table}[htbp]
    \centering
    \caption{Cross-sectional Decomposition of Countries' Log Import Value}
    \begin{tabular}[t]{lcccccc}
    \toprule
    \textit{log type:} &  \multicolumn{2}{c}{Coniferous}&  \multicolumn{2}{c}{Non-conif Non-tropical}&  \multicolumn{2}{c}{Non-conif tropical}\\
    \midrule
      & (1) & (2) & (3) & (4) & (5) & (6)\\
      \textit{Dependent Var:}& Links & Average & Links & Average & Links & Average \\
    \midrule
    log(Import Value) & \num{0.389}*** & \num{0.611}*** & \num{0.437}*** & \num{0.563}*** & \num{0.479}*** & \num{0.521}***\\
    & (\num{0.008}) & (\num{0.008}) & (\num{0.009}) & (\num{0.009}) & (\num{0.017}) & (\num{0.017})\\
   \midrule
   Num.Obs. & \num{141} & \num{141} & \num{136} & \num{136} & \num{80} & \num{80}\\
   R2 & \num{0.916} & \num{0.964} & \num{0.923} & \num{0.952} & \num{0.882} & \num{0.899}\\
   \bottomrule
   \multicolumn{7}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
   \end{tabular}
   \label{tab:decomp_imp}
   \end{table}

   \textit{\textbf{Fact5:} Trade flow is sensitive to the distance between importer and exporter.}.\\
   In general, as the distance between two countries increases, the volume of trade between them decreases (\cite{allen201813}). To examine this relationship in the trade of roundwood, I regress the following regression, what is called, ``Gravity Equation'', with panel data over 2001 to 2018:
   \begin{align}
    \log v_{i \to j, t} = \beta_0 + \beta_1 \log d_{i \to j} + \delta_{i, t} + \gamma_{j, t} + \varepsilon_{i,j,t}
   \end{align}
   where $v_{i \to j, t}$ represents export value from country $i$ to $j$ at year $t$ and $d_{i \to j}$ is a time in-variant bilateral distance between $i$ and $j$. Table \ref{tab:summary_stat} suggests that the elasticity of distance is $-0.7 \sim -2$, which indicates that 1\% increase in the distance between two countries results in a $-0.7 \sim -2$ \% decrease in the trade value between them. This value is consistent with \cite{allen201813}.

   \begin{table}[htbp]
    \caption{Cross-sectional Gravity Equation of Log Export Value}
    \centering
    \begin{tabular}{lccc}
       \tabularnewline \midrule \midrule
       Dependent Variable: & \multicolumn{3}{c}{log(Export Value)}\\
       \midrule
       \textit{log type: } & Coniferous & Non-conif Non-tropical & Non-conif Tropical\\
       Model:                             & (1)            & (2)            & (3)\\  
       \midrule
       \emph{Variables}\\
       log(distance)                         & -1.916$^{***}$ & -1.226$^{***}$ & -0.6735$^{***}$\\   
       & (0.1864)       & (0.1215)       & (0.0907)\\   
        \midrule
        \emph{Fixed-effects}\\
        year-exporter  & Yes            & Yes            & Yes\\  
        year-importer   & Yes            & Yes            & Yes\\  
        \midrule
        \emph{Fit statistics}\\
        Observations                       & 17,124         & 22,695         & 9,494\\  
        R$^2$                              & 0.51745        & 0.47173        & 0.60015\\  
        Within R$^2$                       & 0.21867        & 0.15971        & 0.06400\\  
        \midrule \midrule
        \multicolumn{4}{l}{\emph{Clustered (exporter country and importer country) standard-errors in parentheses}}\\
        \multicolumn{4}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
    \end{tabular}
 \end{table}

@@

Thus, Iobtain 
\begin{align}
    q_1^* = \frac{4 a c_{2} c_{3} + 2 a c_{2} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4} \\
    q_2^* = \frac{4 a c_{1} c_{3} + 2 a c_{1} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4} \\
    q_3^* = \frac{4 a c_{1} c_{2} + 2 a c_{1} + 2 a c_{2} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4}
\end{align}

Next, let us consider the situation where country $3$ bans its log export and supplier $3$ exits from the market. Then, how will supplier $1$ and $2$ react? Since $q_3$ is fixed at $0$, the profit function of supplier $1$ and $2$ are

>>>>

\title{Oasis or Mirage? \\ \large{Trade Network Propagation of Deforestation}}
\author{Tomoki Nishiyama\footnote{Department of Economics, the University of Tokyo. \\ e-mail address: nishiyama-tomoki@g.ecc.u-tokyo.ac.jp \\ I thank Yasuyuki Sawada (a main advisory professor of this thesis), Michihiro Kandori, and all the participants of their seminar for helpful discussion. I am also grateful to Shotaro Beppu, Yutao Chen, and Yuto Iwamoto for meaningful comments and supports.}}
\date{January 2024}
\maketitle

\begin{abstract}
    Log production is destroying forests around the world and contributing to global warming. To address deforestation, various countries have begun to adopt policies to restrict log exports. However, even if one country restricts log exports, the countries that have been importing logs may increase their log production to compensate for their previous imports. It is also possible that other countries will increase their log exports to the log consuming countries. In this case, one country's log export restrictions could induce deforestation in other countries through trade networks. In this paper, I focus on two policies, Russia's log export restrictions in 2007 and Myanmar's log export ban in 2014, to demonstrate how these policies affect the log industry in other countries through trade networks. I find that when one country restricts log exports, log production increases in their previously main export destination and trade competitors who supply logs to the same market. This result suggests that through a network of trade, one country's pro-environmental policies can cause environmental damage in other countries.
\end{abstract}

\textit{
    A king is wandering in the desert to find a clue to reforestation. There used to be a forest in this desert. However, due to the mass production of logs, the former forest has been lost and has become a desert. The once cool forest is now a scorching desert with no water to be found no matter how far one walks. The king, who is about to collapse, finds something like water in the distance. The king says, ``There is an oasis spreading out over there. There must be water. There must be trees. We can regenerate the forest from there." And he starts running. But, is that water really an oasis? Is it not a mirage?
}
\section{Introduction}
Deforestation is an urgent issue on this planet. 1.48 million $km^2$ tropical forests was destroyed since 2001, which is equivalent to an area larger than sum of France, Spain, and Germany (\cite{balboni2023economics}). Deforestation is causing devastation of the global environment. Deforestation accounts for 12-20\% of global greenhouse gas emissions, as it reduces the capacity to absorb carbon dioxide through plants' photosynthesis and contributes to climate change (\cite{van2009co2}). Deforestation also causes loss of biodiversity because forests are home to a wide variety of plants and animals. The extraction of timber to produce forest products is one of the main causes of deforestation. To address this serious problem, some countries have banned log exports since the 1980s. For example, Myanmar, which has destroyed half of its tropical forests since 1960 and worked as the world's third largest supplier (FAOSTAT (2023)), banned log exports in 2014. \\

@@

Using annual trade flow and production data of forestry industries, I employ shift-share design to empirically demonstrate effects of supply shock triggered by the ban of log exports. I regress outcome of each country on how much the country is exposed to the supply shock. The exposure to the shock is measured with interaction of two parts. The first part called ``shift'' is a measure of how much export-restricting country reduces their export to the rest of the world with the restriction. The second part called ``share'' is a measure of how much each country has been dependent on a specific market or industry before the restriction. Combining these two parts, I obtain measure of how much each country is exposed to the Russia or Myanmar's export restriction policy. By using this shift-share approach, I find that when log export restrictions are imposed in a country, log production increases in the country with the larger exposure to that supply shock, i.e., the country that was the export-restricting country's major export destination. This indicates that a country's log export restrictions contribute to deforestation in its major trading partners. On the other hand, for countries that exported to markets similar to that export-restricting country, there was no significant response in terms of production, export volume, or export value to the export-restriction shock. These results suggest that an pro-environmental policy in one country to protect its own forest has effect to propagate deforestation to their previous trade partners. This implicates that an efficacy of one country's forest protection can be crowded out by the spillover effects. It emphasizes that one government policy to protect its own forest is not sufficient to tackle with global environmental issue.\\

@@

As for the empirical method to examine propagation of a supply shock, I refer to recent growing literature of network analysis in economics. \cite{acemoglu2012network} firstly introduces the analysis of how shock on an agent propagates to the other agents throughout network between agents. Based on this strand, various papers discuss how a shock to a specific firms affects the other firms that do not directly suffer from the shock through production supply chain. For example, \cite{barrot2016input} and \cite{carvalho2021supply} examine how shocks of the Eastern Japan Great Earthquake affects firms that are located far from the damaged area through their supply chain networks. I follow synthetic DID of \cite{xu2017generalized} and shift-share approach of \cite{huneeus2018production} to empirically show the network propagation effects of one country's pro-environmental policy on the other countries.\\

The remainder of this paper is organized as follows. Section 2 describes how I construct trade network flow data for forest products. Section 3 provides an overview of two trade restriction policies (Russia in 2007 and Myanmar in 2014) and explains how these policies are exogeneous shocks for other countries. Section 4 presents a sketch of the network data to give an overall picture of the trade network. Based on some basic facts explained in Section 4, Section 5 presents a simple model for constructing hypotheses on how one country's policy affects other countries. Based on the theoretical predictions, Section 6 and 7 presents empirical results. Section 6 describes impacts of export restriction policy on the country's log trade partners. Then, Section 7 presents impacts on trade competitors that supply logs to the Russia's (or Myanmar's) trade partners. Section 8 discusses interpretation of the empirical results and concludes the discussion. Additional empirical results are in the appendix.\\

@@

\begin{figure}[H]
    \centering
    \caption{Aggregated time-series data of Roundwood Production and Export Quantity}
    \subfigure[][Production Quantity]{\includegraphics*[bb=0 0 800 650, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/summary_stat/production.png"}}
    \subfigure[][Export Quantity]{\includegraphics*[bb=0 0 800 650, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/summary_stat/exp_quant.png"}}
    \label{fig:time_series}
\end{figure}

@@

\subsection{Russia's log export restriction in 2007}
Russia developed the largest coniferous forest in the world, the Siberian ``taiga'', which accounted for half of the world's supply of coniferous wood.  To cope with the deforestation and to promote domestic wood processing industry, Russian government imposed an export tax of 6.5\% in July 2007, rising to 20\% on July 2007 and 25\% in April 2008 on logs exported from Russia (\cite{lin2017incidence}). This restriction on log exports was introduced due to the Russian domestic situation. Additionally, as \cite{meti} points out, the new Russian Forest Code, which was base of these export tax policies, was founded in December 2006. This haste of policy interventions supports my assumption that the policy was exogeneous shock for the rest of the world. \\

Figure \ref{fig:shock_russia} shows significance of this Russian supply shock. Panel (a) represents time-series of import price, import quantity, and import value for coniferous roundwood. First, let us see Panel (a). Each gray line represents the average price at which roundwood produced in each country is imported into the rest of the world. The blue line represents the average price at which roundwood produced in Russia is imported into countries other than Russia. In the same way, Panels (b) and (c) show the average import volume and total import value, respectively, of roundwood produced in each country and imported into the rest of the world.

Panel (a) shows that Russia's restriction on log exports in 2007 increases the average price of roundwood imports from Russia about 1.1 $\sim$ 1.4 times. This increase is consistent with the export tax rate. In addition to the effect on price, Panel (b) describes that the policy dramatically reduces the average quantity of roundwood imports from Russia by almost half. Panel (c) shows the policy leads to a rapid decrease in value of imports from Russia. In other words, the export restriction policy in 2007 has significant impact on the supply from Russia to the rest of the world market.

@@

I can consider this export ban as an exogenous supply shock for the rest of the world. That is because the prohibition was due to the situation of Myanmar's country, which is not related to the other countries' situation. Fig \ref{fig:shock_Myanmar} shows significance of the supply shock. Panel A represents time-series of import price, import quantity, and import value for non-coniferous and non-tropical roundwood. First, let us see Panel A. Each gray line represents the average price at which roundwood produced in each country is imported into the rest of the world. The blue line represents the average price at which roundwood produced in Myanmar is imported into countries other than Myanmar. In the same way, Panels B and C show the average import volume and total import value, respectively, of roundwood produced in each country and imported into the rest of the world.\\

@@

\section{Sketch of the Trade Network of Logs}

This section provides descriptive statistics to convey whole picture of the trade network data. Figure \ref{fig:export_network} shows the export network of roundwoods. Hereafter, I present several descriptive discussions which clarify the characteristics of these trade networks. First, I show cross-sectional summary statistics of roundwoods in 2018 with Table \ref{tab:summary_stat}. The summary statistics of roundwood export / import prices are presented in Table \ref{tab:summary_stat_price} in the Appendix. Based on these summary statistics, I presents several facts which describe the trade networks.\\

\begin{figure}[H] 
    \centering
    \caption{Trade Network of Roundwood Export Values in 2010}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 450 450, scale=0.3]{"~/OneDrive - The University of Tokyo/deforestation/fig/network/nontrop_conif.png"}}
    \subfigure[][Non-coniferous]{\includegraphics*[bb=0 0 450 450, scale=0.3]{"~/OneDrive - The University of Tokyo/deforestation/fig/network/nontrop_nonconif.png"}}
    \subfigure[][Tropical]{\includegraphics*[bb=0 0 450 450, scale=0.3]{"~/OneDrive - The University of Tokyo/deforestation/fig/network/tropical.png"}}
    \caption*{\small{Each green line shows the trade flow of roundwood export value between two countries. The thickness of the line represents the amount of export value.}}
    \label{fig:export_network}
\end{figure}

@@

\textit{\textbf{Fact 1:} Most of the roundwood production are supplied to the domestic market.} \\
Table \ref{tab:summary_stat} shows that around 10\% of the roundwood production are used for international trade and the rest 90\% are consumed in the domestic market. Figure \ref{tab:summary_stat_price} shows the long term trend of production and export of roundwoods. In any period, around 90 \% of the production is consumed in the domestic market\footnote{There is a jump in the export quantity of non-coniferous non-tropical roundwood in 2004. This might be due to errors of the original FAOSTAT dataset.}.\\

@@

\textit{\textbf{Fact 2:} Roundwood is used as intermediate inputs of forestry products.} \\
Roundwood is used as intermediate input goods of various forestry product, such as sawn wood, plywood, pulp, and wood chip. Table \ref{tab:intermediate_input} shows relationship between quantity of forestry products made in each country and quantity of roundwood produced for domestic market and roundwood imported from foreign suppliers. As a control, I include lagged GDP on the right-hand side. There are positive relationship between quantity of roundwoods and quantity of forestry products. This result is consistent with the fact that roundwoods are used as intermediate inputs of forestry products.\\

@@

 \textit{\textbf{Fact3:} The distribution of active export / import links (links with positive export / import quantity) is right-skewed.}\\
 I construct bipartite graph consisted of around 160 importer countries and 160 exporter countries. However, not all the links between potential importer countries and exporter countries are not active. In other words, some countries do not export roundwood at all to some other countries. To examine the number of active links of roundwood trade, I present histograms in Figure \ref{fig:num_of_trade_links}. First, in both export and import of any roundwood, the distribution has a long tail on the right side. In addition, the number of countries with zero links are larger in exports than in imports. This is consistent with the uneven distribution of forest resources over countries due to different climate or areas.\\

 \begin{figure}[H]
    \centering
    \caption{Number of Roundwood Trade Links in 2018}
    \subfigure[][Export Links]{\centering \includegraphics*[bb=0 0 1000 600, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/num_links/num_links_exp.png"}}
    \subfigure[][Import Links]{\centering \includegraphics*[bb=0 0 1000 600, scale=0.2]{"~/OneDrive - The University of Tokyo/deforestation/fig/num_links/num_links_imp.png"}}
    \caption*{\small{The left panel is a histogram of number of links for roundwood exports, and the right panel is a histogram of number of links for roundwood imports. The unit is country-level, and there are 164 countries for coniferous roundwood, 166 countries for non-coniferous non-tropical roundwood, and 160 countries for non-coniferous tropical roundwood.}}
    \label{fig:num_of_trade_links}
\end{figure}

@@

The results of this decomposition in 2018 are displayed in Table \ref{tab:decomp_exp} and \ref{tab:decomp_imp}. ``Links'' indicates a esimate of $\beta_1$ and ``Average'' indicates a estimate of $\beta_2$. These results suggest that around $50 \sim 60$ \% of the variation of the export (import) value is explained by the variation of average export (import) value per link. In other words, more than half of the variation of the export (import) comes from variation of the intensive margin.\\

\begin{table}[htbp]
    \centering
    \caption{Cross-sectional Decomposition of Countries' Log Export Value}
    \begin{tabular}[t]{lcccccc}
    \toprule
    \textit{log type:} &  \multicolumn{2}{c}{Coniferous}&  \multicolumn{2}{c}{Non-conif Non-tropical}&  \multicolumn{2}{c}{Non-conif tropical}\\
    \midrule
      & (1) & (2) & (3) & (4) & (5) & (6)\\
      \textit{Dependent Var:}& Links & Average & Links & Average & Links & Average \\
    \midrule
    log(Export Value)  & \num{0.390}*** & \num{0.610}*** & \num{0.412}*** & \num{0.588}*** & \num{0.379}*** & \num{0.621}***\\
    & (\num{0.010}) & (\num{0.010}) & (\num{0.010}) & (\num{0.010}) & (\num{0.013}) & (\num{0.013})\\
   \midrule
   Num.Obs. & \num{95} & \num{95} & \num{120} & \num{120} & \num{102} & \num{102}\\
   R2 & \num{0.899} & \num{0.956} & \num{0.919} & \num{0.959} & \num{0.894} & \num{0.957}\\
   \bottomrule
   \end{tabular}
   \caption*{\small{Heteroskedasticity robust standard-errors are reported in parentheses. Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}
   \label{tab:decomp_exp}
   \end{table}

\begin{table}[htbp]
    \centering
    \caption{Cross-sectional Decomposition of Countries' Log Import Value}
    \begin{tabular}[t]{lcccccc}
    \toprule
    \textit{log type:} &  \multicolumn{2}{c}{Coniferous}&  \multicolumn{2}{c}{Non-conif Non-tropical}&  \multicolumn{2}{c}{Non-conif tropical}\\
    \midrule
      & (1) & (2) & (3) & (4) & (5) & (6)\\
      \textit{Dependent Var:}& Links & Average & Links & Average & Links & Average \\
    \midrule
    log(Import Value) & \num{0.389}*** & \num{0.611}*** & \num{0.437}*** & \num{0.563}*** & \num{0.479}*** & \num{0.521}***\\
    & (\num{0.008}) & (\num{0.008}) & (\num{0.009}) & (\num{0.009}) & (\num{0.017}) & (\num{0.017})\\
   \midrule
   Num.Obs. & \num{141} & \num{141} & \num{136} & \num{136} & \num{80} & \num{80}\\
   R2 & \num{0.916} & \num{0.964} & \num{0.923} & \num{0.952} & \num{0.882} & \num{0.899}\\
   \bottomrule
   \end{tabular}
   \caption*{\small{Heteroskedasticity robust standard-errors are reported in parentheses. Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}
   \label{tab:decomp_imp}
   \end{table}

   \textit{\textbf{Fact5:} Trade flow is sensitive to the distance between importer and exporter.}.\\
   In general, as the distance between two countries increases, the volume of trade between them decreases (\cite{allen201813}). To examine this relationship in the trade of roundwood, I regress the following regression, what is called, ``Gravity Equation'', with panel data over 2001 to 2018:
   \begin{align}
    \log v_{i \to j, t} = \beta_0 + \beta_1 \log d_{i \to j} + \delta_{i, t} + \gamma_{j, t} + \varepsilon_{i,j,t}
   \end{align}
   where $v_{i \to j, t}$ represents export value from country $i$ to $j$ at year $t$ and $d_{i \to j}$ is a time in-variant bilateral distance between $i$ and $j$. Table \ref{tab:summary_stat} suggests that the elasticity of distance is $-0.7 \sim -2$, which indicates that 1\% increase in the distance between two countries results in a $-0.7 \sim -2$ \% decrease in the trade value between them. This value is consistent with \cite{allen201813}. I also estimate the gravity equation with cross-sectional data and report how the coefficient changes over time in Figure \ref{fig:gravity_dynamic} in the Appendix. The results suggests that elasticity is quite stable over time in the trade of roundwoods.\\

   \begin{table}[htbp]
    \caption{Cross-sectional Gravity Equation of Log Export Value}
    \centering
    \begin{tabular}{lccc}
       \tabularnewline \midrule \midrule
       Dependent Variable: & \multicolumn{3}{c}{log(Export Value)}\\
       \midrule
       \textit{log type: } & Coniferous & Non-conif Non-tropical & Non-conif Tropical\\
       Model:                             & (1)            & (2)            & (3)\\  
       \midrule
       \emph{Variables}\\
       log(distance)                         & -1.916$^{***}$ & -1.226$^{***}$ & -0.6735$^{***}$\\   
       & (0.1864)       & (0.1215)       & (0.0907)\\   
        \midrule
        \emph{Fixed-effects}\\
        year-exporter  & Yes            & Yes            & Yes\\  
        year-importer   & Yes            & Yes            & Yes\\  
        \midrule
        \emph{Fit statistics}\\
        Observations                       & 17,124         & 22,695         & 9,494\\  
        R$^2$                              & 0.51745        & 0.47173        & 0.60015\\  
        Within R$^2$                       & 0.21867        & 0.15971        & 0.06400\\  
        \midrule \midrule
    \end{tabular}
    \caption*{\small{Clustered (exporter country and importer country)standard-errors are reported in parentheses. Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}
 \end{table}

@@

Thus, I obtain 
\begin{align}
    q_1^* = \frac{4 a c_{2} c_{3} + 2 a c_{2} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4} \\
    q_2^* = \frac{4 a c_{1} c_{3} + 2 a c_{1} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4} \\
    q_3^* = \frac{4 a c_{1} c_{2} + 2 a c_{1} + 2 a c_{2} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4}
\end{align}

\subsection{Effect of One Supplyer Exit}
Next, let us consider the situation where country $3$ bans its log export and supplier $3$ exits from the market. Then, how will supplier $1$ and $2$ react? Since $q_3$ is fixed at $0$, the profit function of supplier $1$ and $2$ are
